%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Venilton}{FalvoJr}{ \urlstyle{same}
\href{mailto:falvojr@gmail.com}{falvojr@gmail.com} \\ +55 16 99721-8281
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Sao Paulo}
\descript{PhD in Computer Engineering}
\location{Exp. 2020 | Sao Carlos, SP, Brazil}
Special Student\\
\location{ Cum. GPA: 4.0 / 4.0}
\sectionsep
\descript{Msc in Computer Engineering}
\location{Apr 2015 | Sao Carlos, SP, Brazil}
\location{ Cum. GPA: 3.77 / 4.0}
\sectionsep

\subsection{UNIARA}
\descript{BS in Computer Engineering}
\location{Dec 2011 | Araraquara, SP, Brazil}
\location{ Cum. GPA: 3.26 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/falvojr}{\bf falvojr} \\
LinkedIn://  \href{https://www.linkedin.com/in/falvojr}{\bf falvojr}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Project Management \\
Software Design + Practicum \\
Software Dev. + Practicum \\
Software Maintenance \\
User Requirements Definition \\
\sectionsep

\subsection{Undergraduate}
Cloud Computing \\
Artificial Intelligence \\
Human Computer Interaction \\
Software Architecture \\
Software Testing and Validation \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Expertise:}
Ajax \textbullet{} Android \textbullet{} API Design \textbullet{} C\# \\
Express \textbullet{} Git \textbullet{} Gradle \textbullet{} Hibernate \\
HTML \& CSS \textbullet{} Java EE \textbullet{} JavaScript \\
JPA \textbullet{} Maven \textbullet{} Node.js \textbullet{} REST \\ 
Spring Framework\textbullet{} SQL \\
\location{Working Knowledge:}
AngularJS \textbullet{} AWS \textbullet{} Docker \textbullet{} Gulp \\
Jenkins \textbullet{} Kotlin \textbullet{} Microservices \\
NoSQL \textbullet{} Vagrant\\
\location{Familiar:}
C/C++ \textbullet{} Objective-C \textbullet{} Subversion \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Cast Group}
\descript{| Technology Specialist }
\location{Oct 2008 - Present | Araraquara, SP, Brazil}
Design the most appropriate software architecture to business needs, meeting the requirements and constraints of stakeholders. Has a leadership and mentoring roles, working on developing the team's technical skills.\\
Currently implements RESTful APIs with Spring Boot, using the modules: Spring MVC, Spring Security, Spring HATEOAS and Spring Data (REST and JPA). Moreover, HTML, CSS, JavaScript and AngularJS are used for Single Page Applications (SPA). On the other hand, mobile development is predominantly native on Android and iOS platforms.
\sectionsep

\runsubsection{Brain Machine}
\descript{| Co-Founder }
\location{Feb 2016 - Present | Araraquara, SP, Brazil}
Collaborator in the projects of this startup, specialized in new development trends and coaching.
\sectionsep

\runsubsection{IFSP}
\descript{| Substitute Teacher }
\location{Mar 2016 - Jun 2017 | Araraquara, SP, Brazil}
Teach to higher and technical education at Federal Institute of Education, Science and Technology of Sao Paulo (IFSP).
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Digio}
\descript{| Cast Group | Banco CBSS}
\location{Oct 2016 – Mar 2017 | Barueri, SP, Brazil}
Digio is a fintech that offers a Visa credit card with all the management through mobile applications. Available for \textbf{\href{https://goo.gl/zvebsh}{Android}} and iOS.\\
\textit{Confidential architecture.}
\sectionsep

\runsubsection{The Dining Club}
\descript{| Brain Machine}
\location{Feb 2016 – Jul 2016 | Brisbane, QLD, Australia}
\textbf{\href{https://www.thediningclub.com.au}{The Dining Club}} is a company/website with australian restaurants offers and exclusive discounts to your subscribers.\\
This project use the MEAN stack (MongoDB, Express, AngularJS and Node.js) to build an API, administrative portal and public website. Furthermore, it was configured a strategy of the continuous delivery with Docker and Amazon EC2.
\sectionsep

\runsubsection{Ourocard}
\descript{| Cast Group | Banco do Brasil}
\location{Sep 2015 – Dec 2015 | Brasilia, DF, Brazil}
Pioneering project in the use of Host Card Emulation (HCE) through NFC technology in Brazil and first solution of the world launched by a bank to mobile payments with multiple cards (debit and credit). Available for \textbf{\href{https://goo.gl/T7oLwj}{Android}} and iOS.\\
\textit{Confidential architecture.}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 
\begin{tabular}{rll}
2016 & Oracle & Java SE 6 Programmer Certified Professional \\
2013 & Microsift & MS: Programming in HTML5 with JavaScript and CSS3 \\
2011 & Microsift & MCPD: Web Developer 4 \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \sectionsep
% \sectionsep
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
